### 2014-07-09 paper/designspace.tex
update figures with new routings

\subsection{Path Constraints}
Depending on the purpose of the pipe, its geometry may be constrained to specific locations within the 3D model. An \emph{endpoint-constrained} pipe requires specific start and end points, but the particular route of the internal path is irrelevant. This is the case for circuit schematics, where the electronic components have fixed locations, but many routing solutions are valid. In contrast, for a \emph{path-constrained} pipe the shape of the path is important. For example, threading electroluminescent (EL) wire through a clear pipe enables makers to emulate neon art (Figure \ref{fig:teaser}, right). A \emph{fully constrained} pipe requires specific terminals as well as a specific path. If a maker wishes the EL wire to exit the rear of the sign to hide the electronics, she can use a fully-constrained path (Figure \ref{fig:teaser}, right). Finally, an \emph{unconstrained} pipe does not need a specific path or terminal points. A cavity to modify an object's overall weight is an example of an unconstrained pipe (Figure \ref{fig:openings}c).

>>>>

\subsection{Path Constraints}
Depending on the purpose of the pipe, its geometry may be constrained to specific locations within the 3D model. An \emph{endpoint-constrained} pipe requires specific start and end points, but the particular route of the internal path is irrelevant. This is the case for circuit schematics, where the electronic components have fixed locations, but many routing solutions are valid. In contrast, for a \emph{path-constrained} pipe the shape of the path is important. For example, threading electroluminescent (EL) wire through a clear pipe enables makers to emulate neon art (Figure \ref{fig:teaser}, right). A \emph{fully constrained} pipe requires specific terminals as well as a specific path. If a maker wishes the EL wire to exit the rear of the sign to hide the electronics, she can use a fully-constrained path (Figure \ref{fig:teaser}, right). Pipes may also be fully \emph{unconstrained}, however in this paper we focus on contexts where designers deliberately place constraints on pipe endpoints or path.

### 2014-07-09 paper/introduction.tex
update figures with new routings

Recently, human-computer interaction researchers have begun to explore how to prototype interactive objects using additive 3D printing processes.
Existing approaches, including Printed Optics \cite{Willis-printedoptics} and Sauron \cite{Savage-sauron}, exclusively focus on optical sensing and visual displays --- we seek to grow the vocabulary of supported tangible input and output modalities, and we propose using pipes and cavities, allowing designers to integrate secondary materials post-print, for this purpose.

>>>>

Recently, human-computer interaction researchers have begun to explore how to prototype interactive objects using additive 3D printing processes.
\changes{Existing approaches, including Printed Optics \cite{Willis-printedoptics} and Sauron \cite{Savage-sauron}, exclusively focus on optical sensing and visual displays --- we seek to grow the vocabulary of supported tangible input and output modalities, and we propose using pipes and cavities, allowing designers to integrate secondary materials post-print, for this purpose.}

### 2014-07-09 paper/tubes.tex
update figures with new routings

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/routing-tests.png}
\caption{\changes{A set of example routings produced by our tool.  Note that because the initial state of the discrete rod is based on an A* routing, it cannot ``jump around'' holes in a genus $>0$ mesh (a) to route on the other side, even if this would reduce overall bending.  Pipes successfully route through long, curving paths in knots (b), and multiple pipes placed in a single mesh in a tangled configuration successfully avoid each other (c).}}
\label{fig:complex}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/routing-tests.png}
\caption{\changes{A set of example routings produced by our tool.  Note that there is a tradeoff between bending and length of pipes: our pipes prefer shortness, however pipes could "jump around" holes in genus $> 0$ meshes (a) to reduce bending.  Pipes successfully route through long, curving paths in knots (b), and multiple pipes placed in a single mesh in a tangled configuration successfully avoid each other (c).}}
\label{fig:complex}
\end{figure}
